\textbf{Supplementary Materials}\\ A Critical Appraisal of the Zero-Multiple Method: Structural, Thermodynamic, Dielectric, and Dynamical Properties of a Water System

### 2014-12-05 writedown/zm/paper.water/si.tex
partially finish revising

\title{\textbf{Supplementary Materials}\\
  A Critical Appraisal of the Zero-Multiple Method: Structural,
Thermodynamic, Dielectric, and Dynamical Properties of a Water System}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\affiliation{CAEP Software Center for High Performance Numerical Simulation, Huayuan Road
6, 100088 Beijing, China}
\affiliation{Zuse Institute Berlin (ZIB), Germany}
\author{Ikuo Fukuda}
\email{ifukuda@protein.osaka-u.ac.jp}
\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita,
Osaka 565-0871, Japan}
\affiliation{RIKEN (The Institute of Physical and Chemical Research), 2-1 Hirosawa, Wako,
Saitama 351-0198, Japan}
\author{Haruki Nakamura}
\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita,
Osaka 565-0871, Japan}

@@

@@

>>>>

\title{\textbf{Supplementary Materials}\\
  A Critical Appraisal of the Zero-Multiple Method: Structural,
Thermodynamic, Dielectric, and Dynamical Properties of a Water System}
\author{Han Wang}
\email{wang_han@iapcm.ac.cn}
\affiliation{CAEP Software Center for High Performance Numerical Simulation, Huayuan Road
6, 100088 Beijing, China}
\affiliation{Zuse Institute Berlin (ZIB), Germany}
\author{Ikuo Fukuda}
\email{ifukuda@protein.osaka-u.ac.jp}
\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita,
Osaka 565-0871, Japan}
\affiliation{RIKEN (The Institute of Physical and Chemical Research), 2-1 Hirosawa, Wako,
Saitama 351-0198, Japan}
\author{Haruki Nakamura}
\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita,
Osaka 565-0871, Japan}

@@

\begin{figure}[]
\centering
\includegraphics[width=0.5\textwidth]{fig/result.nvt/fig-press.eps}\\
\caption{A typical pressure trajectory. Simulated with system $L_1$ and SPME electrostatic method.}
\label{fig:pres-l1}
\end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt/fig-rdf-cutoff.eps}\\
\caption{  The comparison between the RDF calculated by RF method with group and atom cut-off schemes.
The results of SPME and ZM $l=1$ are also presented for comparison.}
\label{fig:gkr-conv-alpha}
\end{figure}
